Irt plot extra

### 2022-02-22 manuscript.Rmd
Descriptive table is updated with footnote

```{r reltab2, results='asis'}
relevant.scale.data %>% 
apa_table(landscape =T,caption ="List of instruments measuring related consttucts to LEBA", format = "latex",escape = T, font_size = "footnotesize", align = c("p{3cm}", rep("p{3.6cm}", ncol(relevant.scale.data))))

@@

    missing = "no"
    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
  modify_caption("Demographic Characteristics") -> desc_table

@@

colnames(descriptives) <- c("Items", "Mean", "SD", "Skew", "Kurtosis", "SW Statistics", "Item Total Correlation")

@@

```{r tabDes,results='asis'}
descriptives2 %>% 
apa_table(landscape =T,caption ="Descriptive Statistics", escape =F, font_size = "footnotesize", note = "*p<.001", align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(descriptives2)))) 
```

>>>>

```{r reltab2, results='asis'}
relevant.scale.data %>% 
apa_table(landscape =T,caption ="List of instruments measuring related constucts to LEBA", format = "latex",escape = T, font_size = "footnotesize", align = c("p{3cm}", rep("p{3.6cm}", ncol(relevant.scale.data))))

@@

    missing = "no"
    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
  modify_caption("Demographic Characteristics of Partinipants (n=690)") -> desc_table

@@

colnames(descriptives) <- c("Items", "Mean", "SD", "Skew", "Kurtosis", "$SW^{1}$", "Item Total Correlation")

@@

```{r tabDes,results='asis'}
descriptives2 %>% 
apa_table(landscape =T,caption ="Univariate Descriptive Statistics for the 48 Items. All Items Violated Univariate Normality Assumption Assessed by Shapiro–Wilk (SW) Test. The  Item-total Correlation Ranges Between .03-.48", escape =F, font_size = "footnotesize", note = ("$*p<.001$, $^{1}Shapiro–Wilk$ $Statistics$"), align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(descriptives2)))) 
```
